\section{Experience}

\cvEntry{Senior Fullstack Developer}{Oct 2024 - Present}{Cometa}{Remote (Ciudad de México, México)}
\begin{itemize}
  \item Member of Cometa's \textbf{finance engineering team}. Own payins, payouts, and billing / invoicing flows end-to-end across a Django modular monolith and Next.js frontend.
  \item Built \textbf{Argus}, a Rust read-only Redshift proxy (Axum, lambda\_http on AWS Lambda + API Gateway) powering the Guardian Credit Scoring flow: whitelisted tables, identity-based row filtering, pagination, and thread-safe credential refresh.
  \item Delivered the billing + inventory domain: cart payment lifecycle state machine, batch-only inventory reservation pipeline, cart-expiration via cross-module outbox events, Gandalf-authenticated endpoints, and Postgres indexes on hot paths.
  \item Shipped Guardian Stripe checkout end-to-end (PaymentIntent, per-currency minimum-amount drawer, locale-aware errors, a11y) across Django backend and Next.js frontend.
  \item Built MCP servers exposing Cometa's domain APIs as LLM-callable tools; shipped full-stack features on a Django modular monolith + Next.js (Clean Architecture, DDD) with on-call triage, Alembic migrations, and report-query tuning.
\end{itemize}

\cvEntry{Senior Software Engineer}{Sep 2023 - Oct 2024}{Foris}{Remote}
\begin{itemize}
  \item Built Airflow DAGs and an in-house DSL for data pipelines on AWS Glue, S3, and Athena.
  \item Shipped Python backend services for academic planning and course
        scheduling products; led technical design reviews and mentored
        mid-level engineers.
\end{itemize}

\cvEntry{Director of Software Engineering}{Jan 2023 - Sep 2023}{Artificio}{Remote}
\begin{itemize}
  \item Shipped an end-to-end image-search service for \textbf{Seezlo} (artwork discovery): deployed vision models on AWS SageMaker and an image-embedding RAG for artwork retrieval, exposed via FastAPI.
  \item Led the engineering function end-to-end: hiring, roadmap, and architecture direction for Python services on AWS.
\end{itemize}

\cvEntry{Python Backend Engineer}{Oct 2021 - Jan 2023}{SpaceAG Global}{Lima, Perú}
\begin{itemize}
  \item Implemented a multi-tenant reporting module syncing AWS RDS with AWS Athena via EventBridge, Celery, and Pandas, producing Parquet files on S3.
  \item Scaled the Postgres master on Aurora Serverless v2 with read replicas; built AWS Lambda health-checks wired into Slack, Sentry, and Google Sheets.
  \item Shipped Django/Flask APIs on AWS Lambda (Serverless, Zappa); exposed a legacy Microsoft Access DB through API Gateway + DynamoDB and integrated weather stations (WeatherLink v2, Metos 2.0, Adcon).
\end{itemize}

\cvEntry{Backend Developer \& DevOps}{Jan 2020 - Dec 2021}{Alfi}{Remote}
\begin{itemize}
  \item Rebuilt the core application from scratch in Django and modeled all REST APIs; production stack on AWS ECS/Fargate, RDS, ElastiCache (Redis), and RabbitMQ.
  \item Led the backend team: story points, code reviews, and PRs.
\end{itemize}

\cvEntry{Co-founder \& Backend Engineer}{Jan 2017 - Jan 2020}{Chaty}{Lima, Perú}
\begin{itemize}
  \item Co-founded a multi-tenant SaaS for restaurant-chain chat ordering; integrated Facebook Messenger, WhatsApp, and Telegram APIs for chatbot-driven order flows.
  \item Integrated multiple payment gateways for end-to-end checkout and automated shipping assignment + order routing on PostGIS.
\end{itemize}

\cvEntry{Software Architect}{Oct 2014 - Jan 2017}{Ventorystack}{Remote}
\begin{itemize}
  \item Designed and implemented a real-time inventory system on Tornado,
        MongoDB, AWS Lambda, and AWS SQS.
\end{itemize}

\cvEntry{Earlier roles: Django edtech, embedded systems, ML research}{2011 - 2015}{Crehana (CTO), DGNEST (Founder), Engitronic, CTIC-UNI}{Lima, Perú}
